\documentclass{subfile}

\begin{document}
	\chapter{The Buffalo Way}\label{ch:buffalo}
	\index{The buffalo way}\emph{The buffalo way} is a \emph{bashing} method of solving inequality problems. It usually exploits symmetry or cyclic property and involves tedious calculations, so it is not always elegant. Nonetheless it is a useful tool. The idea is to assume something like $a\leq b\leq c$ without losing any generality, specially when there is symmetry. In general, we want to assume that
		\begin{align*}
			a_1
				& \leq a_2\leq\cdots\leq a_n\\
			a_2
				& = a_1+b_1\\
				& \vdots\\
			a_n
				& = a_1+b_n
		\end{align*}
	We can also assume the following.
		\begin{align*}
			a_2
				& = a_1+c_1\\
			a_3
				& = a_2+c_2\\
				& = a_1+c_1+c_2\\
				& \vdots\\
			a_n
				& = a_{n-1}+c_{n-1}\\
				& = a_1+c_1+\ldots+c_{n-1}
		\end{align*}
	where $c_1,\ldots,c_{n-1}\geq0$. Out of these two forms, the latter is actually a consequence of the former one and is usually the more used one. We will see a few problems that implement this technique.
		\begin{problem}
			Prove that for two non-negative reals $x,y$
				\begin{align*}
					x+y
						& \geq2\sqrt{xy}
				\end{align*}
		\end{problem}
	
		\begin{solution}
			Since the inequality is symmetric on $x$ and $y$, we can assume without loss of generality that $x\leq y$. Let $y=x+k$.
				\begin{align*}
					x+y
						& \geq2\sqrt{xy}\\
					\iff2x+k
						& \geq2\sqrt{x(x+k)}\\
					\iff4x^2+4xk+k^2
						& \geq4x^2+4xk\\
					\iff k^2
						& \geq0
				\end{align*}
			which is evident.
		\end{solution}
	Try proving the case $n=3$ of arithmetic-geometric mean inequality with this technique. You will understand why we said this is often a tedious technique.
		\begin{problem}
			\begin{align*}
				x+y+z
					& \geq3\sqrt[3]{xyz}
			\end{align*}
		\end{problem}
	Let us also prove the following using buffalo way.
		\begin{problem}
			Let $a,b,c>0$ be real numbers. Prove that
				\begin{align*}
					a^2+b^2+c^2
						& \geq ab+bc+ca
				\end{align*}
		\end{problem}
	
		\begin{solution}
			Assume that $a\leq b\leq c$ and $b=a+x,c=a+x+y$ where $x,y\geq0$.
				\begin{align*}
					a^2+(a+x)^2+(a+x+y)^2
						& \geq a(a+x)+(a+x)(a+x+y)+(a+x+y)a\\
					\iff 3a^2+2x^2+y^2+4ax+2xy+2ay
						& \geq 3a^2+x^2+4ax+2ay+2xy\\
					\iff x^2+y^2
						& \geq0
				\end{align*}
			This is again true.
		\end{solution}
	
		\begin{problem}
			Let $a,b,c\geq0$ be real numbers such that $a\leq b\leq c$. Prove that
				\begin{align*}
					(a+b)(c+a)^2
						& \geq6abc
				\end{align*}
		\end{problem}
	
		\begin{solution}
			Since $a\leq b\leq c$, let $b=a+x,c=a+x+y$.
				\begin{align*}
					(2a+x)(2a+x+y)^2
						& \geq6a(a+x)(a+x+y)\\
					\iff(2a+x)(4a^2+x^2+y^2+4ax+4ay+2xy)
						& \geq6a(a^2+2ax+x^2+ay+xy)\\
					\iff8a^3+12a^2x+8a^2y+6ax^2+8axy+2ay^2+x^3+2ax^2+xy^2
						& \geq6a^3+12a^2+6ax^2+6a^2y+6axy\\
					\iff 2a^3+2a^2y+2axy+2ay^2+x^3+2x^2y+xy^2
						& \geq0
				\end{align*}
			This evidently true.
		\end{solution}
	Now, we will prove Nesbitt's inequality using the first form of the buffalo way.
		\begin{proof}[Proof of Nesbitt's inequality by the buffalo way]
			Let $x\leq y\leq z$ and $y=x+a,z=y+b$ with $a\geq0,b\geq0$. We are required to prove that
				\begin{align*}
					\dfrac{x}{y+z}+\dfrac{y}{z+x}+\dfrac{z}{x+y}
						& \geq\dfrac{3}{2}
				\end{align*}
			Let us express each variable as a parameter of a single variable.
				\begin{align*}
					\dfrac{y-a}{2y+b}+\dfrac{y}{2y+b-a}+\dfrac{y+b}{2y-a}
						& \geq\dfrac{3}{2}\\
					\iff\dfrac{y-a}{2y+b}-\dfrac{1}{2}+\dfrac{y}{2y+b-a}-\dfrac{1}{2}+\dfrac{y+b}{2y-a}-\dfrac{1}{2}
						& \geq0\\
					\iff\dfrac{1}{2}\left(\dfrac{2y-2a-2y-b}{2y+b}+\dfrac{2y-2y-b+a}{2y+b-a}+\dfrac{2y+2b-2y+a}{2y-a}\right)
						& \geq0\\
					\iff-\dfrac{2a+b}{2y+b}+\dfrac{a-b}{2y+b-a}+\dfrac{2b+a}{2y-a}
						& \geq0
				\end{align*}
			The last inequality actually holds because of the following:
				\begin{align*}
					\dfrac{2b+a}{2y-a}+\dfrac{a-b}{2y+b-a}-\dfrac{2a+b}{2y+b}
						& \geq\dfrac{2b+a}{2y+b-a}+\dfrac{a-b}{2y+b-a}-\dfrac{2a+b}{2y+b}\\
						& \geq\dfrac{2a+2b}{2y+b-a}-\dfrac{2a+b}{2y+b}\\
						& \geq\dfrac{2a+2b}{2y+b}-\dfrac{2a+b}{2y+b}\\
						& = \dfrac{a}{2y+b}
				\end{align*}
			which is obviously at least $0$. Here, we have used the facts that $\frac{1}{x}\geq\frac{1}{y}$ implies $\frac{1}{x-u}\geq\frac{1}{y}$ and $\frac{1}{x}\geq\frac{1}{y+v}$ for $u,v\geq0$.
		\end{proof}
	The next inequality is a nice application of the buffalo way.
		\begin{problem}
			Let $x,y,z>0$ be real numbers such that no two are equal. Show that,
				\begin{align*}
					\dfrac{1}{(x-y)^2}+\dfrac{1}{(y-z)^2}+\dfrac{1}{(z-x)^2}
						& \geq\dfrac{4}{xy+yz+zx}
				\end{align*}
		\end{problem}
	
		\begin{solution}
			The expression on the left is symmetric on $x,y,z$. Without loss of generality, assume that $x\leq y\leq z$ and $y=x+a,z=x+a+b$.
				\begin{align*}
					\dfrac{1}{a^2}+\dfrac{1}{b^2}+\dfrac{1}{(a+b)^2}
						& \geq\dfrac{4}{x(x+a)+(x+a)(x+a+b)+(x+a+b)x}\\
						& = \dfrac{4}{x^2+xa+x^2+2ax+a^2+bx+ab+x^2+xa+bx}\\
						& \geq \dfrac{4}{3x^2+4xa+2xb+ab+a^2}
				\end{align*}
			Note that there is no $x$ on the left side of the inequality. So, we can use $x>0$ to get rid of it.
				\begin{align*}
					3x^2+4xa+2xb+ab+a^2
						& > ab+a^2\\
					\dfrac{4}{3x^2+4xa+2xb+ab+a^2}
						& <\dfrac{4}{ab+a^2}
				\end{align*}
			So, we are done if we can prove the following.
				\begin{align*}
					\dfrac{1}{a^2}+\dfrac{1}{b^2}+\dfrac{1}{(a+b)^2}
						& \geq\dfrac{4}{ab+a^2}\\
						& = \dfrac{4}{a(b+a)}
				\end{align*}
			This is not a trivial inequality. We have to show that this actually holds.
				\begin{align*}
					\dfrac{1}{a^2}+\dfrac{1}{b^2}-\dfrac{2}{a(b+a)}+\dfrac{1}{(a+b)^2}
						& \geq\dfrac{2}{a(b+a)}\\
					\iff\dfrac{1}{b^2}+\left(\dfrac{1}{a}-\dfrac{1}{a+b}\right)^2
						& \geq\dfrac{2}{a(a+b)}\\
					\iff\dfrac{1}{b^2}+\left(\dfrac{b}{a(a+b)}\right)^2
						& \geq\dfrac{2}{a(a+b)}\\
					\iff\dfrac{1}{b^2}+\dfrac{b^2}{a^2(a+b)^2}
						& \geq\dfrac{2}{a(a+b)}
				\end{align*}
			The last inequality is true by arithmetic-geometric mean inequality since
				\begin{align*}
					\dfrac{1}{b^2}+\dfrac{b^2}{a^2(a+b)^2}
						& \geq2\sqrt{\dfrac{1}{b^2}\cdot\dfrac{b^2}{a^2(a+b)^2}}\\
						& = \dfrac{2}{a(a+b)}
				\end{align*}
		\end{solution}
	Solve the next problem as an exercise.
		\begin{problem}
			For all real $x,y,z\geq0$, prove that
				\begin{align*}
					\dfrac{x^3+y^3+z^3}{x^2y+y^2z+z^2x}
						& \geq\sum\dfrac{x}{y+z}-1
				\end{align*}
		\end{problem}
\end{document}