\documentclass{subfile}

\begin{document}
	\section[Jensen and Popoviciu]{Convexity, Jensen and Popoviciu's Inequality}\label{sec:convexity}
	A function $f:I\to\mathbb{R}$ is called \index{Jensen convex}\textit{Jensen convex} on some interval $I=[a,b]$ if for any $x,y\in I$,
		\begin{align*}
			f\left(\dfrac{x+y}{2}\right)
				& \leq \dfrac{f(x)+f(y)}{2}
		\end{align*}
	$f$ is \textit{Jensen concave} if $-f$ is Jensen convex. Similarly, a sequence of real numbers $(a_{n})$ is \textit{Jensen convex} if
		\begin{align*}
			2a_{n}
				& \leq a_{n-1}+a_{n+1}
		\end{align*}
	holds for $n\in\mathbb{N}$. This concept of convexity was formally introduced first by \textcite{jensen_1905, jensen_1906}. Jensen also proved the following result.
		\begin{theorem}\label{thm:jensenrational}
			Let $w_{1},\ldots,w_{n}$ be non-negative rational numbers in the interval $I$ such that $w_{1}+\ldots+w_{n}=1$ and $f$ be a Jensen convex function on $I$. Then
				\begin{align*}
					f(w_{1}x_{1}+\ldots+w_{n}x_{n})
						& \leq w_{1}f(x_{1})+\ldots+w_{n}f(x_{n})
				\end{align*}
		\end{theorem}
	But the idea itself was not completely new. \textcite{holder_1889} proved \autoref{thm:jensenrational} under the condition that $f$ can be differentiated at least twice and $f''(x)\geq 0$. Ironically, this is exactly the convexity condition from calculus point of view.
	
	Let $f$ be a convex function. For a vector $\mathbf{x}$, let $f(\mathbf{x})$ be the vector $(f(x_{1}),\ldots,f(x_{n}))$.
		\begin{theorem}[\itshape Weighted Jensen's inequality]\label{thm:weightedjensen}
			Let $f$ be a convex function. For a vector $\mathbf{x}$ of real numbers in the domain of $f$ and a weight vector $\omega$,
				\begin{align*}
					f\left(\mathfrak{A}(\mathbf{x},\omega)\right)
						& \leq \mathfrak{A}(f(\mathbf{x}),\omega)
				\end{align*}
		\end{theorem}
	
		\begin{theorem}[\itshape Petrovic's Inequality]
			Let $f$ be a convex function and $(x_{n})$ be a sequence of positive real numbers. Then
				\begin{align*}
					f(x_{1})+\ldots+f(x_{n})
						& \leq f(x_{1}+\ldots+x_{n})+(n-1)f(0)
				\end{align*}
		\end{theorem}
	
		\begin{theorem}[\itshape Huygen's inequality]
			Let $\mathbf{x}$ be a vector with $n$ elements and $\omega$ be a weight vector. Then
				\begin{align*}
					\prod_{i=1}^{n}(1+x_{i})
						& \geq \mathfrak{G}(\mathbf{x})
				\end{align*}
		\end{theorem}
	Note that this is just a special case of \nameref{thm:holder}.
		\begin{theorem}[\itshape Popoviciu's inequality]
			Let $f$ be a convex function in the interval $[a,b]$. For any $x,y,z\in[a,b]$,
				\begin{align*}
					f\left(\dfrac{x+y+z}{3}\right)+\dfrac{f(x)+f(y)+f(z)}{3}
						& \geq \left(f\left(\dfrac{x+y}{2}\right)+f\left(\dfrac{y+z}{2}\right)+f\left(\dfrac{z+x}{2}\right)\right)
				\end{align*}
		\end{theorem}
\end{document}