\documentclass{subfile}

\begin{document}
	\section{IMO}\label{sec:imo}
	
		\begin{problem}[IMO $1995$, problem $2$]
			Let $a,b,c$ be real numbers such that $abc=1$. Prove that
				\begin{align*}
					\dfrac{1}{a^{3}(b+c)}+\dfrac{1}{b^{3}(c+a)}+\dfrac{1}{c^{3}(a+b)}
						& \geq\dfrac{3}{2}
				\end{align*}
		\end{problem}
	
		\begin{problem}[IMO $1999$, problem $2$]
			Let $n\geq2$ be an integer. Find the least constant $C$ such that
				\begin{align*}
					\sum_{1\leq i < j\leq n}x_{i}x_{j}(x_{i}^{2}+x_{j}^{2})
						& \leq C\left(\sum_{i=1}^{n}x_{i}\right)^{4}
				\end{align*}
			holds for all non-negative real numbers $x_{1},\ldots,x_{n}$. When does equality occur?
		\end{problem}
	
		\begin{problem}[IMO $2000$, problem $2$]
			Let $a,b,c$ be positive real numbers such that $abc=1$. Prove that
				\begin{align*}
					\left(a-1+\dfrac{1}{b}\right)\left(b-1+\dfrac{1}{c}\right)\left(c-1+\dfrac{1}{a}\right)
						& \leq1
				\end{align*}
		\end{problem}
		
		\begin{problem}[IMO $2001$, problem $2$]
			Let $a,b,c$ be positive real numbers. Prove that
				\begin{align*}
					\dfrac{a}{\sqrt{a^{2}+8bc}}+\dfrac{b}{\sqrt{b^{2}+8ca}}+\dfrac{c}{\sqrt{c^{2}+8ab}}
						& \geq1
				\end{align*}
		\end{problem}
		
		\begin{problem}[IMO $2003$, problem $5$]
			Let $n$ be a positive integer and $x_{1}\leq\ldots\leq x_{n}$ be real numbers. Prove that
				\begin{align*}
					\left(\sum_{i,j=1}^{n}|x_{i}-x_{j}|\right)^{2}
						& \leq \dfrac{2(n^{2}-1)}{3}\sum_{i,j=1}^{n}(x_{i}-x_{j})^{2}
				\end{align*}
			Show that equality holds if and only if $x_{1},\ldots,x_{n}$ forms an arithmetic sequence.
		\end{problem}
	
		\begin{problem}[IMO $2004$, problem $4$]
			Let $n\geq3$ be an integer. Let $t_{1},\ldots,t_{n}$ be positive real numbers such that
				\begin{align*}
					n^{2}+1
						& > (t_{1}+\ldots+t_{n})\left(\dfrac{1}{t_{1}}+\ldots+\dfrac{1}{t_{n}}\right)
				\end{align*}
			Show that $t_{i},t_{j},t_{k}$ are the sides of a triangle for all $1\leq i< j < k\leq n$.
		\end{problem}
	
		\begin{problem}[IMO $2005$, problem $3$]
			Let $x,y,z$ be real numbers such that $xyz\geq1$. Prove that
				\begin{align*}
					\dfrac{x^{5}-x^{2}}{x^{5}+y^{2}+z^{2}}+\dfrac{y^{5}-y^{2}}{x^{2}+y^{5}+z^{2}}+\dfrac{z^{5}-z^{2}}{x^{2}+y^{2}+z^{5}}
						& \geq0
				\end{align*}
			
				\begin{solution}
					We have already solved it in \autoref{prob:imo2005-3}.
				\end{solution}
		\end{problem}
		
		\begin{problem}[IMO $2006$, problem $3$]
			Determine the least real number $M$ such that the inequality
				\begin{align*}
					\left|ab\left(a^{2}-b^{2}\right)+bc\left(b^{2}-c^{2}\right)+ca\left(c^{2}-a^{2}\right)\right|
						& \leq M(a^{2}+b^{2}+c^{2})^{2}
				\end{align*}
			holds for all real numbers $a,b,c$.
		\end{problem}
	
		\begin{problem}[IMO $2008$, problem $2$]
			Let $x,y,z\neq1$ be real numbers such that $xyz=1$. Prove that
				\begin{align*}
					\dfrac{x^{2}}{(x-1)^{2}}+\dfrac{y^{2}}{(y-1)^{2}}+\dfrac{z^{2}}{(z-1)^{2}}
						& \geq1
				\end{align*}
			Also, prove that equality holds for infinitely many rational $x,y,z$ such that $xyz=1$ and $x,y,z\neq1$.
		\end{problem}
	
		\begin{problem}[IMO $2012$, problem $2$]
			Let $n\geq3$ be a positive integer and $a_2,\ldots,a_n$ be positive real numbers such that $a_1\cdots a_n=1$. Prove that
				\begin{align*}
					(1+a_2)^{2}\cdots(1+a_n)^{n}
						& \geq n^{n}
				\end{align*}
		\end{problem}
	
		\begin{problem}[IMO $2020$, problem $2$]
			Let $a,b,c,d$ be positive real numbers such that $a\geq b\geq c\geq d$ and $a+b+c+d=1$. Prove that
				\begin{align*}
					(a+2b+3c+4d)a^{a}b^{b}c^{c}d^{d}
						& < 1
				\end{align*}
			
				\begin{solution}
					Since $a+b+c+d=1$, by \nameref{thm:weightedpowermean} on $\omega=(a,b,c,d)$ and $\mathbf{a}=(a,b,c,d)$,
						\begin{align*}
							a\cdot a+b\cdot a+c\cdot c+d\cdot d
								& \geq a^{a}b^{b}c^{c}d^{d}
						\end{align*}
					So it is enough to prove that
						\begin{align*}
							(a+2b+3c+4d)(a^{2}+b^{2}+c^{2}+d^{2})
								& \leq (a+b+c+d)^{3}
						\end{align*}
					Expanding these we can easily see that the inequality has to follow. But we can prove it in a smarter way.
						\begin{align*}
							(a+b+c+d)^{3}
								& = (a+b+c+d)\left(a^{2}+b^{2}+c^{2}+d^{2}+2\sum ab\right)
						\end{align*}
					where the sum runs over all possible $\binom{4}{2}$ pairs. Then
						\begin{align*}
							(a+2b+3c+4d)(a^{2}+b^{2}+c^{2}+d^{2})
							& < (a+b+c+d)^{3}\\
							\iff (b+2c+3d)(a^{2}+b^{2}+c^{2}+d^{2})
								& < 2(a+b+c+d)\left(\sum ab\right)
						\end{align*}
					Now, using $a\geq b\geq c$,
						\begin{align*}
							a^{2}+b^{2}+c^{2}+d^{2}
								& \leq a(a+b+c+d)
						\end{align*}
					So, it is enough to show that
						\begin{align*}
							a(b+2c+3d)(a+b+c+d)
								& \leq  2(a+b+c+d)\left(\sum ab\right)\\
							\iff a(b+2c+3d)
								& \leq 2\sum ab\\
							\iff 3da
								& \leq ab+2ca\\
							\iff da+da+da
								& \leq ab+ca+ca
						\end{align*}
					This inequality obviously holds.
				\end{solution}
			
				\begin{remark}
					We could also use \nameref{thm:weightedjensen} after using the fact that $\log(x)$ is concave. The buffalo way works here as well. But the calculation is not going to be pretty if you go that way. This problem was highly criticized within some forums such as the Art of Problem Solving. It was the first inequality problem at the IMO since $2012$. A lot of people thought that the days of inequality at the IMO was over. But when this problem appeared at the IMO $2020$, many people complained and expressed their disappointment that the \textit{no inequality problem at the IMO} streak was finally broken with such a problem.
				\end{remark}
		\end{problem}
	
		\begin{problem}[IMO Shortlist $2015$, A1]
			Let $a,b,c$ be positive real numbers such that $\min\{ab,bc,ca\}\geq1$. Prove that
				\begin{align*}
					\sqrt[3]{(a^2+1)(b^2+1)(c^2+1)}
						& \leq\left(\dfrac{a+b+c}{3}\right)^2+1
				\end{align*}
		\end{problem}
	
		\begin{problem}[IMO Shortlist $2015$, A8]
			Determine the largest real number $a$ such that for all $n\geq1$ and for all real numbers $x_{0},\ldots,x_{n}$ satisfying
				\begin{align*}
					0
						& = x_{0}<x_{1}<\ldots<x_{n}
				\end{align*}
			we have
				\begin{align*}
					\dfrac{1}{x_{1}-x_{0}}+\dfrac{1}{x_{2}-x_{1}}+\ldots+\dfrac{1}{x_{n}-x_{n-1}}
						& \geq a\left(\dfrac{2}{x_{1}}+\dfrac{3}{x_{2}}+\ldots+\dfrac{n+1}{x_{n}}\right)
				\end{align*}
		\end{problem}
	
		\begin{problem}[IMO Shortlist $2018$, A7]
			Find the maximal value of
				\begin{align*}
					S
						& = \sqrt[3]{\dfrac{a}{b+7}}+\sqrt[3]{\dfrac{c}{d+7}}+\sqrt[3]{\dfrac{d}{a+7}}
				\end{align*}
			where $a,b,c,d$ are non-negative real numbers which satisfy $a+b+c+d=100$.
		\end{problem}
\end{document}